AD Target Gene Report

### 2020-04-27 code/03-Run.Rmd

```{r yamlIMPT, eval = T, include=T}
print(getwd())
#Assign your YAML formated config file to a varable
configuration <- "configs/EmoryTargets.yaml"
config <- read_yaml(file=paste0('./',configuration))

>>>>

```{r yamlIMPT, eval = T, include=T}
print(getwd())
#Assign your YAML formated config file to a varable

configuration <- "configs/EmoryTargets.yaml"
configuration <- "configs/TestConfig.yaml"
config <- read_yaml(file=paste0('./',configuration))
